---
title: "Final Assessment"
output: html_notebook
editor_options: 
  markdown: 
    wrap: 72
---

## Final Exam/Summative Assessment

Complete the tasks below using the data provided. Use the existing code
chunks, adding more if needed. Be sure your code is well-formatted and
commented appropriately.

You are allowed to liberally copy and paste from the course
notes/bookdown. There is no need to reinvent the wheel. You'll need to
tweak things here or there to address the specific questions, but for
the watershed delineation, fdc, and HBV parts, there is a LOT you can
copy and paste from the course notes!

Load the required packages here:

```{r}

```

## Part 1: McDonald Hollow

We are just starting to work at a new watershed monitoring station in
McDonald Hollow on Brush Mountain outside Blacksburg and need to do some
preliminary data analysis. Produce the following items to help describe
the site.

### a. A map of the watershed that drains to the station. (20 pts)

The coordinates of the station are roughly 37.24, -80.483. There is a
DEM of the area in the Data folder. It has already been prepared for
hydrologic analysis (filled and breached).

Show the watershed outline on this map over some sort of basemap that
allows us to see terrain. This could be a hillshade or a default basemap
from an open repository.

```{r}

```

### b. Make some plots of stage and specific conductivity. 

hint: you will have to join these two datasets to do this. Also, there
is some bad data at the start of the stage dataset (intentionaly left
for you :-)). The pressure transducer data was not being corrected with
barometric pressure for a while, so there are stage values that are far
too high (in the 9 m range). Be sure to filter out that time period.
Additionally, filter out any Conductivity values above 60
microsiemens/cm.

Data prep: You'll use "McDonald_Conductivity.csv" and
"McDonald_Stage.csv" in the Data folder

Conductivity is in units of microsiemens per centimeter **(10 points)**

```{r}

```

### Plots to create:

Stage and Specific Conductivity v. Time use facets or a composite plot.
**(10 pts)**

```{r}

```

A flow duration curve using the stage data. Be careful with your axis
labels. **(10 pts)**

```{r}

```

Stage (x) plotted against specific conductivity (y). **(10 pts)**

```{r}

```

## Part 2: HBV Calibration

Calibrate the HBV model for watershed 3 at Hubbard Brook (same time
period as in class) using the snow melt data set rather than discharge.
Use a 1000 run Monte Carlo to do this.

For your best model run, calibrated to snow melt, calculate the NSE for
discharge.

Prep Data for the Model and load HBV function: **(10 pts)**

```{r}

```

Calibrate HBV on snow with 1000 run monte carlo: **(10 pts)**

\*Note: In the monte carlo in the bookdown, Use cbind to add Qobs. In
this version you need to add Qobs1, because it has a DATE column. This
allows you to bring in the snow data by joining on the DATE column.

```{r}

```

### Make two plots:

a.  Observed vs. Modeled discharge **(5 pts)**

    ```{r}

    ```

b.  Observed vs. Modeled snow **(5 pts)**

    ```{r}

    ```

And provide the snow NSE and the discharge NSE. **(5 pts)**

### Answer the following question:

Was the discharge NSE better or worse than when we calibrated on
discharge? Why do you think this is? **(5 pts)**
